---
title: "Manuscript: Resistance screening assay for aerial blight"
author: "Sara Thomas-Sharma"
date: "2024-04-19"
output: 
  html_document: 
    number_sections: yes
    theme: readable
    toc: TRUE
    toc_float: TRUE
---

```{r, include=FALSE}
# get working directory
getwd()
```

```{r setup, include=FALSE}
# All necessary packages are assumed to be installed. 
#Loading necessary packages 
library("devtools")
library("poppr")
library("pegas")
library("magrittr")
library("lattice")
library("mmod")
library("ape")
library('dplyr')
library('ggplot2')
library('dplyr')
library('agricolae') # for AUDPC
library('tidyverse')
library('ggpubr')
library('car')
library('spearmanCI')
library('psych')
library('ggpattern')
# for multiple comparisons and compact letter display
library('emmeans')
library('multcomp')
library('multcompView')
#to build linear model or linear mixed effects model
library('lme4')
library('lmerTest')
library ("broom") # includes function tidy
```


# Analysis of microsatellite data

Data and analysis used to generate Table 3 and Figure 3

```{r}
#Loading data
KensyMS <- read.genalex("GenAlex_Results_Kensy_correctedv2.csv", ploidy = 2)

#Running analysis to check different indexes (included in Table 3) 
popdata <- poppr(KensyMS)
popdata

#Figure 3. Minimum Spanning Network
partial_clone_sub <- popsub(KensyMS, exclude = character(0))
partial_clone_dist <- diss.dist(partial_clone_sub, percent = FALSE, mat = FALSE)
min_span_net <- poppr.msn(partial_clone_sub, partial_clone_dist, showplot = FALSE, include.ties = TRUE)

set.seed(44)
plot_poppr_msn(KensyMS,
               min_span_net,
               inds = "ALL",
               mlg = FALSE,
               gadj = 3,
               nodescale = 25.25,
               palette = rainbow,
               cutoff = NULL,
               quantiles = FALSE,
               beforecut = TRUE)
```

# Fungicide resistance screening

Data and analysis used to generate Table 4

```{r}


```

# Coreblock variety screening 

Data and analysis used to generate Table 5

```{r}


```


# Analysis of detached leaf assay

Data and analysis used to generate Figure 4


```{r}
#Loading data
Scatter<-read.csv(file = 'Spearman_Virulence assay results.csv')

#Summarizing data

DLAa<-Scatter %>%
  group_by(Trial, Box, Variety, Isolate)%>%
  dplyr::summarise(Avg_PctLesion=mean(pct_sympt))

se <- function(x, na.rm) sd(x)/sqrt(sum(!is.na(x))) 

DLAb<-DLAa %>%
  group_by(Isolate, Variety) %>%
  dplyr::summarise(counts=n(), Avg_PctLesion2=mean(Avg_PctLesion), SE_PctLesion2=se(Avg_PctLesion))

DLAb$Isolate <- factor(DLAb$Isolate, levels=c("Control","AV13","Avoy1","RT1","ML1","DL24","AC2"))
DLAb$Variety <- factor(DLAb$Variety, levels=c("AG53x9","DP3589"))

#Creating graph
p9<-ggplot(data=DLAb, aes(factor(Isolate), y=Avg_PctLesion2, fill=as.factor(Variety))) + 
  geom_bar(stat="identity", position = "dodge",color='black')+
  labs(x = "Isolate", y = "Disease severity (%)", fill="Variety")+
  geom_errorbar(aes(ymin=Avg_PctLesion2-SE_PctLesion2, ymax=Avg_PctLesion2+SE_PctLesion2), width=.2,position=position_dodge(.9))+
  facet_grid(~Variety)+
  scale_fill_grey()

p9+theme(axis.text.x=element_text(size=20,angle = 45, vjust = 1, hjust=1, face="bold", color = "black"),
         axis.text.y= element_text(size=20,  face="bold", color = "black"),
         axis.title=element_text(size=20, face="bold"))

#ANOVA Sorting Trial 1
Trial1<-DLAa %>%
  filter(Trial=='1')

Trial1$Variety<- as.factor(Trial1$Variety)
Trial1$Isolate <- as.factor(Trial1$Isolate)

#ANOVA TRIAL 1 Pct Symptomatic

Trial1_PctSymptomatic_summary <- Trial1 %>%  group_by(Variety, Isolate) %>%
  summarise(mean=mean(Avg_PctLesion), 
            se=se(Avg_PctLesion)) %>%
  arrange(desc(mean))

Trial1.aov<- aov(Avg_PctLesion ~ Variety + Isolate + Variety:Isolate , data=Trial1)
summary.aov(Trial1.aov)

#Anova(Trial1.aov, type = "III")

#Tukey's HSD  mean separation
Trial2_final_tukey <- TukeyHSD(Trial1.aov)
tukey.cld.Trial2_final <- multcompLetters4(Trial1.aov, Trial2_final_tukey)
cldTrial2_final <- as.data.frame.list(tukey.cld.Trial2_final$`Isolate:Variety`)

Trial1_PctSymptomatic_summary$Tukey <- cldTrial2_final$Letters
print(Trial1_PctSymptomatic_summary)

#1

Trial1_PctSymptomatic_summary_Isolate <- Trial1 %>%  group_by(Isolate) %>%
  summarise(mean=mean(Avg_PctLesion), 
            se=se(Avg_PctLesion)) %>%
  arrange(desc(mean))

Trial1.aov<- aov(Avg_PctLesion ~ Isolate, data=Trial1)
summary.aov(Trial1.aov)

#Anova(Trial1.aov, type = "III")

#Tukey's HSD  mean separation
Trial2_final_tukey <- TukeyHSD(Trial1.aov)
tukey.cld.Trial2_final <- multcompLetters4(Trial1.aov, Trial2_final_tukey)
cldTrial2_final <- as.data.frame.list(tukey.cld.Trial2_final$`Isolate`)

Trial1_PctSymptomatic_summary_Isolate$Tukey <- cldTrial2_final$Letters

#Trial 1

#2 AG53x9

Trial1_PctSymptomatic_summary_VarietyIsolate <- Trial1 %>%  group_by(Variety, Isolate) %>%
  summarise(mean=mean(Avg_PctLesion), 
            se=se(Avg_PctLesion)) %>%
  arrange(desc(mean))

AG53x9_Trial1<-Trial1_PctSymptomatic_summary_VarietyIsolate %>%
  filter(Variety=='AG53x9')

DP3589_Trial1<-Trial1_PctSymptomatic_summary_VarietyIsolate %>%
  filter(Variety=='DP3589')

AG53x9.aov<- aov(Avg_PctLesion ~ Isolate, data=Trial1)
summary.aov(AG53x9.aov)

#Tukey's HSD  mean separation
Trial1_final_tukey_AG53x9 <- TukeyHSD(AG53x9.aov)
tukey.cld.Trial2_final <- multcompLetters4(AG53x9.aov, Trial1_final_tukey_AG53x9)
cldTrial2_final <- as.data.frame.list(tukey.cld.Trial2_final$`Isolate`)
AG53x9_Trial1$Tukey <- cldTrial2_final$Letters
print(AG53x9_Trial1)

DP3589.aov<- aov(Avg_PctLesion ~ Isolate, data=Trial1)
summary.aov(DP3589.aov)

#Tukey's HSD  mean separation
Trial1_final_tukey_DP3589 <- TukeyHSD(DP3589.aov)
tukey.cld.Trial2_final <- multcompLetters4(DP3589.aov, Trial1_final_tukey_DP3589)
cldTrial2_final <- as.data.frame.list(tukey.cld.Trial2_final$`Isolate`)
DP3589_Trial1$Tukey <- cldTrial2_final$Letters
print(DP3589_Trial1)

#Trial 2

Trial1_tukey <- TukeyHSD(Trial1.aov)
tukey.cld.Trial1 <- multcompLetters4(Trial1.aov, Trial1_tukey)
cldTrial1 <- as.data.frame.list(tukey.cld.Trial1$`Variety:Isolate`)
Trial1_PctSymptomatic_summary$Tukey <- cldTrial1$Letters
print(Trial1_PctSymptomatic_summary)


#ANOVA Sorting Trial 2
Trial2<-DLAa %>%
  filter(Trial=='2')

Trial2$Variety<- as.factor(Trial2$Variety)
Trial2$Isolate <- as.factor(Trial2$Isolate)


#ANOVA TRIAL 1 Pct Symptomatic

Trial2_PctSymptomatic_summary <- Trial2 %>%  group_by(Variety, Isolate) %>%
  summarise(mean=mean(Avg_PctLesion), 
            se=se(Avg_PctLesion)) %>%
  arrange(desc(mean))

Trial2.aov<- aov(Avg_PctLesion ~ Variety * Isolate, data=Trial2)
summary.aov(Trial2.aov)

#Anova(Trial1.aov, type = "III")

#Tukey's HSD  mean separation
Trial2_tukey <- TukeyHSD(Trial2.aov)
tukey.cld.Trial2 <- multcompLetters4(Trial2.aov, Trial2_tukey)
cldTrial2 <- as.data.frame.list(tukey.cld.Trial1$`Variety:Isolate`)
Trial2_PctSymptomatic_summary$Tukey <- cldTrial2$Letters
print(Trial2_PctSymptomatic_summary)


```

# Analysis of inoculum levels

Data and analysis used to generate Figure 5


```{r}
#Load data
InoculumData<-read_csv(file = 'New_4_Data_low_inoculum_levels_both_trial_1_trial_2.csv', na=c(".", "NA")) 

AB_IL1<- InoculumData %>% 
  mutate (Total_leaves= Num_nodes_pot*3,
          Pct_symptomatic=(Num_symptleaf/Total_leaves)*100,
          Pct_drop=(Num_dropleaf/Total_leaves)*100)

#Summarizing across Variety, DAI and Inoculum amount  
se <- function(x, na.rm) sd(x)/sqrt(sum(!is.na(x))) 

AB_IL1a<- AB_IL1 %>%  
  group_by(Trial, Inoculum_Amount, DAI, Variety)%>%
  summarise(Num_rep= n(),
            Median_DRating=median(Dis_rating),
            Avg_sympleaf=mean(Pct_symptomatic),
            Avg_dropleaf=mean(Pct_drop), 
            SE_sympleaf=se(Pct_symptomatic),
            SE_dropleaf=se(Pct_drop))
#view(AB_IL1a)

#Final day of Assesment 
AB_IL1b<- AB_IL1 %>%  
  group_by(Trial, Variety)%>%
  summarise(Num_rep= n(),
            Med_DRating=median(Dis_rating),
            Avg_Fsympleaf=mean(Pct_symptomatic),
            Avg_Fdropleaf=mean(Pct_drop), 
            SE_Fsympleaf=se(Pct_symptomatic),
            SE_Fdropleaf=se(Pct_drop))

#AUDPC
AB_VS2<- AB_IL1 %>%  
  group_by(Trial, Inoculum_Amount, Variety, Rep)%>%
  mutate (AUDPC_symleaf = audpc(Pct_symptomatic, DAI),
          AUDPC_disrate = audpc(Dis_rating, DAI))


#Summarizing AUDPC value for each Variety
AB_VS2a<- AB_VS2 %>%  
  group_by(Trial, Inoculum_Amount, DAI, Variety)%>%
  summarise(counts= n(),
            Avg_AUDPCSymp=mean(AUDPC_symleaf),
            Avg_AUDPCDR=mean(AUDPC_disrate),
            SE_AUSymL=se(AUDPC_symleaf),
            SE_AUDR=se(AUDPC_disrate))

AB_VS2a2<- AB_VS2 %>%  
  group_by(Trial, Inoculum_Amount, Variety)%>%
  summarise(Avg_AUDPCSymp=mean(AUDPC_symleaf),
            Avg_AUDPCDR=mean(AUDPC_disrate),
            SE_AUSymL=mean(se(AUDPC_symleaf)),
            SE_AUDR=mean(se(AUDPC_disrate)))


#Giving an specific order
AB_VS2a2$Inoculum_Amount <- factor(AB_VS2a2$Inoculum_Amount, levels=c("0", "0.1", "0.5", "2"))

#Graph of inoculum levels
p9<-ggplot(data=AB_VS2a2, aes(factor(Inoculum_Amount), y=Avg_AUDPCSymp, fill=as.factor(Variety))) + 
  geom_bar(stat="identity", position = "dodge",color='black')+
  labs(x = "Amount of inoculum", y = "AUDPC of Percent Disease Severity", fill="Variety")+
  geom_errorbar(aes(ymin=Avg_AUDPCSymp-SE_AUSymL, ymax=Avg_AUDPCSymp+SE_AUSymL), width=.2,position=position_dodge(.9))+
  facet_wrap(~Trial)+
  scale_fill_grey()

p9+theme(axis.text.x=element_text(size=17,angle = 45, vjust = 1, hjust=1, face="bold", color = "black"),
         axis.text.y= element_text(size=17,  face="bold", color = "black"),
         axis.title=element_text(size=17, face="bold"),
         strip.text = element_text(size = 17, face="bold"))


```

# Preliminary screening of seven varieties  

Data and analysis used to generate Figure 6


```{r}
### Step 1: Importing data 
AB_VS<- read_csv (file= 'VarietyScreening_v10_mod.csv',  na=c(".", "NA")) # Use file VarietyScreening_v10_mod.csv

### Step 2: Data manupulation and exploration

AB_VS1<- AB_VS %>% 
  mutate (Total_leaves= Num_nodes_pot*3,
          Pct_symptomatic=(Num_symptleaf/Total_leaves)*100,
          Pct_drop=(Num_dropleaf/Total_leaves)*100)

#Generating new response variable, AUDPC for percent symptomatic leaves and disease rating**
AB_VS2<- AB_VS1 %>%  
  group_by(Trial, Variety, Rep)%>%
  mutate (AUDPC_symleaf = audpc(Pct_symptomatic, DAI),
          AUDPC_disrate = audpc(Dis_rating, DAI))


#function for calculating standard error
se <- function(x, na.rm) sd(x)/sqrt(sum(!is.na(x))) 

AB_VS1a<- AB_VS1 %>%  
  group_by(Trial, DAI, Variety)%>%
  summarise(Num_rep= n(),
            Median_DRating=median(Dis_rating),
            Avg_sympleaf=mean(Pct_symptomatic),
            Avg_dropleaf=mean(Pct_drop), 
            SE_sympleaf=se(Pct_symptomatic),
            SE_dropleaf=se(Pct_drop))

#view(PSL_final)

PSL_final<-AB_VS1 %>%
  filter(DAI=='20' | DAI=='20')

PSL_finala<- AB_VS1 %>%  
  group_by(Trial, Variety)%>%
  summarise(Num_rep= n(),
            Med_DRating=median(Dis_rating),
            Avg_Fsympleaf=mean(Pct_symptomatic),
            Avg_Fdropleaf=mean(Pct_drop), 
            SE_Fsympleaf=se(Pct_symptomatic),
            SE_Fdropleaf=se(Pct_drop))
#function for calculating standard error
se <- function(x, na.rm) sd(x)/sqrt(sum(!is.na(x))) 

#Summarizing AUDPC response variables: AUDPC for disease rating and symptomatic leaves**
AB_VS2a<- AB_VS2 %>%  
  group_by(Trial, DAI, Variety)%>%
  summarise(Num_rep= n(),
            Avg_AUDPCSymp=mean(AUDPC_symleaf),
            Avg_AUDPCDR=mean(AUDPC_disrate),
            SE_AUSymL=se(AUDPC_symleaf),
            SE_AUDR=se(AUDPC_disrate))


AB_VS2ab<- AB_VS2a

#Functions to Reorder bargraphs
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

level<-c("Trial 1","Trial 2")
AB_VS2ab$Trial<-level[AB_VS2ab$Trial]


#Plot of AUDPC of percent symptomatic leaves  5/18/2022
graph4a<-ggplot(AB_VS2ab, aes(x=reorder_within(Variety, -Avg_AUDPCSymp, Trial), y=Avg_AUDPCSymp, fill=Variety))+
  labs(x = "Cultivars", y = "Average AUDPC of percent disease severity")+
  theme(axis.text.x=element_blank(), axis.ticks.x = element_blank())+
  geom_bar(stat='identity', position=position_dodge(0.9))+
  geom_errorbar(aes(ymin=Avg_AUDPCSymp-SE_AUSymL, ymax=Avg_AUDPCSymp+SE_AUSymL), width=.1, position=position_dodge(0.9))+
  scale_x_reordered()+
  facet_wrap(~Trial, scales = "free_x")+
  scale_fill_grey()

graph4a+theme(axis.text.x=element_text(size=12,angle = 45, vjust = 1, hjust=1, face="bold", color = "black"),
              axis.text.y= element_text(size=12,  face="bold", color = "black"),
              axis.title=element_text(size=12, face="bold"),
              strip.text = element_text(size = 12, face="bold"))
```

# Regression analysis

Data and analysis used to generate figures 7 and 8

```{r}
 
#Regression for Height to first true leaf 
AB_CBVS<- read_csv (file= 'Coreblock_all_11_08_2022_mod_v1.csv',  na=c(".", "NA"))
head(AB_CBVS)
str(AB_CBVS)

AUDPC_cor<- AB_CBVS

AUDPC_corK<-AUDPC_cor %>%
  filter(Trial=='Trial_1')
AUDPC_cor1K<-AUDPC_corK %>%
  filter(DAI=='21')
AUDPC_cor2K<-AUDPC_cor %>%
  filter(Trial=='Trial_2')
AUDPC_cor2KD<-AUDPC_cor2K %>%
  filter(DAI=='21')

spearmancorr <- ggscatter(AUDPC_cor1K, x = "Num_symptleaf", y = "Height_toV1",
                          add = "reg.line",  # Add regressin line
                          title = "Trial 1",
                          xlab ="Number of symptomatic leaves", 
                          ylab = "Height to first true leaf (cm)",
                          add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
                          conf.int = TRUE) # Add confidence interval

spearmancorr + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "spearman")+
  font("title",size = 15, face = "bold")+
  font("xlab", size = 15, face = "bold")+
  font("ylab", size = 15, face = "bold")+
  font("xy.text", size = 15, face = "bold")

```

#Supplementary material 

Data and figures used to generate supplementary figure 1

```{r}
#Figures on percentage disease severity in final assessment in the four levels of inouculum tested

#Data should already be loaded ( R object: InoculumData)
AB_IL1<- InoculumData %>% 
  mutate (Total_leaves= Num_nodes_pot*3,
          Pct_symptomatic=(Num_symptleaf/Total_leaves)*100,
          Pct_drop=(Num_dropleaf/Total_leaves)*100)

#Summarizing across Variety, DAI and Inoculum amount  
se <- function(x, na.rm) sd(x)/sqrt(sum(!is.na(x))) 

AB_IL1a<- AB_IL1 %>%  
  group_by(Trial, Inoculum_Amount, DAI, Variety)%>%
  summarise(Num_rep= n(),
            Median_DRating=median(Dis_rating),
            Avg_sympleaf=mean(Pct_symptomatic),
            Avg_dropleaf=mean(Pct_drop), 
            SE_sympleaf=se(Pct_symptomatic),
            SE_dropleaf=se(Pct_drop))

#AUDPC
AB_VS2<- AB_IL1 %>%  
  group_by(Trial, Inoculum_Amount, Variety, Rep)%>%
  mutate (AUDPC_symleaf = audpc(Pct_symptomatic, DAI),
          AUDPC_disrate = audpc(Dis_rating, DAI))

#Graph for percentage disease severity
AB_VS2$Inoculum_Amount <- factor(AB_VS2$Inoculum_Amount, levels=c("0", "0.1", "0.5", "2"))

graph1a<-ggplot(AB_VS2, aes(x=Inoculum_Amount, y=AUDPC_symleaf, fill=Inoculum_Amount))+
  labs(x = "Inoculum amount", y = "Percentage disease severity final day of assessment")+
  geom_boxplot()+
  facet_wrap(~Trial)
plot(graph1a)

#ANOVA
#TRIAL 1
Trial1<-AB_VS2 %>%
  filter(Trial=='1')

Trial1_final<-Trial1 %>%
  filter(DAI=='33')

Trial1$Variety<- as.factor(Trial1$Variety)
Trial1$Inoculum_Amount <- as.factor(Trial1$Inoculum_Amount)
Trial1$DAI <- as.factor(Trial1$DAI)

#ANOVA TRIAL 1 Pct Symptomatic

Trial1_PctSymptomatic_summary <- Trial1 %>%  group_by(Inoculum_Amount) %>%
  summarise(mean=mean(Pct_symptomatic), 
            se=se(Pct_symptomatic)) %>%
  arrange(desc(mean))

Trial1.aov<- aov(Pct_symptomatic ~ Inoculum_Amount, data=Trial1_final)
summary.aov(Trial1.aov)

#Anova(Trial2.aov, type = "III")

#Tukey's HSD  mean separation
Trial1tukey <- TukeyHSD(Trial1.aov)
#tukey.cld.Trial1 <- multcompLetters4(Trial1.aov, Trial1_tukey)
cldTrial1 <- as.data.frame.list(tukey.cld.Trial1$`Inoculum_Amount`)
Trial1_PctSymptomatic_summary$Tukey <- cldTrial1$Letters
print(Trial1_PctSymptomatic_summary)

#TRIAL 2
Trial2<-AB_VS2 %>%
  filter(Trial=='1')

Trial2_final<-Trial2 %>%
  filter(DAI=='33')

Trial2$Variety<- as.factor(Trial2$Variety)
Trial2$Inoculum_Amount <- as.factor(Trial2$Inoculum_Amount)
Trial2$DAI <- as.factor(Trial2$DAI)

#ANOVA TRIAL 1 Pct Symptomatic

Trial2_PctSymptomatic_summary <- Trial2 %>%  group_by(Inoculum_Amount) %>%
  summarise(mean=mean(Pct_symptomatic), 
            se=se(Pct_symptomatic)) %>%
  arrange(desc(mean))

Trial2.aov<- aov(Pct_symptomatic ~ Inoculum_Amount, data=Trial2_final)
summary.aov(Trial2.aov)

#Anova(Trial2.aov, type = "III")

#Tukey's HSD  mean separation
Trial2tukey <- TukeyHSD(Trial2.aov)
#tukey.cld.Trial2 <- multcompLetters4(Trial2.aov, Trial2_tukey)
cldTrial2 <- as.data.frame.list(tukey.cld.Trial2$`Inoculum_Amount`)
Trial2_PctSymptomatic_summary$Tukey <- cldTrial2$Letters
print(Trial2_PctSymptomatic_summary)
```

Data and figures used to generate supplementary figure 2
```{r}

```


Data and figures used to generate supplementary figure 3

```{r}
#PIS screening 
AB_PI<- read_csv (file='PI Seeds Trial_combined_v1_STS.csv',  na=c(".", "NA"), col_types = cols(Variety = col_character())) 
#head(AB_PI)
#str(AB_PI)
#view(AB_PI)
#levels(as.factor(AB_PI$Variety))

#Summarising data across replicates

AB_PI1<- AB_PI %>%  
  group_by(Trial_num, DAI, Variety)%>%
  summarise(Num_rep= n(),
            Median_DRating=median(Rating))

AB_PI2<- AB_PI %>%  
  group_by(Trial_num, Variety, Plant_ID)%>%
  summarise(
    Num_rep= n(),
    AUDPC_disrate = audpc(Rating, DAI))

### Data for plotting ####
AB_PI3<- AB_PI2 %>%  
  group_by(Trial_num, Variety)%>%
  summarise(
    Avg_AUDPC_disrate = mean(AUDPC_disrate),
    SE_AUDR=se(AUDPC_disrate))

graph2b<-ggplot(AB_PI3, aes(x=Variety,Avg_AUDPC_disrate, y=Avg_AUDPC_disrate, fill=Variety))+
  labs(x = "Plant introductions tested", y = "Average AUDPC of disease rating")+
  theme(axis.title.x=element_text(face='bold',size=12), axis.text.x=element_text(face='bold', size=10, angle=25), axis.title.y=element_text(face='bold',size=12, vjust=0.8))+
  guides(fill="none")+
  geom_bar(stat='identity', position=position_dodge())+
  geom_errorbar(aes(ymin=Avg_AUDPC_disrate-SE_AUDR, ymax=Avg_AUDPC_disrate+SE_AUDR), width=.1, position=position_dodge())+
  facet_wrap(~Trial_num)
plot(graph2b)

ABPI_lm<-lm (AUDPC_disrate ~ Variety +Trial_num, data=AB_PI2)
summary(ABPI_lm)
par(mfrow=c(2,2))

# get (adjusted) weight means per group
ABPI_lm_means <- emmeans(object = ABPI_lm, specs = "Variety")

# add letters to each mean
ABPI_lm_means_cld <- cld(object = ABPI_lm_means, adjust = "Tukey", Letters = letters, alpha = 0.05)
ABPI_lm_means_cld

```

# Computational environment
```{r SessionInfo, eval=TRUE, echo=FALSE, results='markup'}
R.Version()$version.string
R.Version()$system
sessionInfo()
```
